\textbf{International Transport costs:\\New Findings from modeling additive costs}\\Online Appendix (Not for Publication)

### 2021-09-13 redaction/JEGeo/revision_JEGeo/revised_article/DHP_JoEG_rev1.tex
Suite comparaison 10/3 - 5/2
Signed-off-by: Guillaume Daudin <gdaudin@mac.com>

\begin{table}[htbp]
 \centering
\caption{Transport costs estimates: summary} \vspace{5mm} \label{tab:summary_results}
	\input{Table1_reshaped.tex}
		\begin{tablenotes}
		\tiny
		\item Statistics are obtained weighting each observation by its value relative to total trade flows.
		\item 1989 trade by air is excluded
		%\item The additive term is expressed in fraction of fas price.
		\item For the  4-digit model, statistics for observed data have been calculated for the same set of years as used for estimation, i.e.
		1974, 1981, 1989, 2001, 2009, 2013, 2017 and 2019
		\item \textbf{Model (a): With ad-valorem transport costs only}
		\item \textbf{Model (b): With additive and ad-valorem transport costs}
	\end{tablenotes}
\end{table}

@@

\subsubsection{XXX}

\textbf{Il me semble qu'on avait dit qu'on mettait une 3e robustesse. Non? Faire une transition pour la suite.}

>>>>

\begin{table}[htbp]
 \centering
\caption{Transport costs estimates: summary} \vspace{5mm} \label{tab:summary_results}
	\input{Table1.tex}
		\begin{tablenotes}
		\tiny
		\item Statistics are obtained weighting each observation by its value relative to total trade flows.
		\item 1989 trade by air is excluded
		%\item The additive term is expressed in fraction of fas price.
		\item For the  4-digit model, statistics for observed data have been calculated for the same set of years as used for estimation, i.e.
		1974, 1981, 1989, 2001, 2009, 2013, 2017 and 2019
		\item \textbf{Model (a): With ad-valorem transport costs only}
		\item \textbf{Model (b): With additive and ad-valorem transport costs}
	\end{tablenotes}
\end{table}

@@

\subsubsection{Robustness to aggregation}

Current data are available at the 10-digit level for products (HS10).
Theoretically, they should be available from 1989. 
But because of the COVID situation, it was only possible to get 1997-1999 and 2001-2019.
Yet, as \ref{tab: baseline10} shows, the results are similar when using 10-digit product and 5-digit products.

\begin{table}[htbp]
	\centering
	\caption{Transport costs estimates: robustess to agregation} \vspace{5mm} \label{tab:baseline10}
	\input{Table_baseline10.tex}
	\begin{tablenotes}
		\tiny
		\item Statistics for 1997-1999 and 2002-2019
		\item Statistics are obtained weighting each observation by its value relative to total trade flows.
		\item \textbf{Model (a): With ad-valorem transport costs only}
		\item \textbf{Model (b): With additive and ad-valorem transport costs}
	\end{tablenotes}
\end{table}

\begin{figure}[htbp]
	\caption{Transport cost time trends: robustness to agregation}
	\label{fig:comp_IV_SITC5}
	\begin{center}
		\includegraphics[height=8cm]{scatter_chronology_baseline_baseline10.png}
	\end{center}
\end{figure}
